This is an example of article title

### 2025-10-30 paper/paper.tex
Fix a wrong title.

    \begin{tikzpicture}
        \begin{axis}[
            grid=major,
            width=.5\textwidth,
            legend style={at={(0.95,0.5)}, anchor=east},
            unit vector ratio=1 1,
            xmin = -1, xmax = 8,
            ymin = -4.25, ymax = 2.25,
            title style={yshift=-.5\baselineskip,},
            title={Two Bézier curves on different Lie groups},
        ] %
            \addplot[only marks, mark=*, mark size=2pt, color=TolMutedSand] coordinates {(-0.5, 0.0)};
            \addlegendentry{$q_1$};
            \addplot[only marks, mark=*, mark size=2pt, color=TolMutedOlive] coordinates {(0.5, 0.0)};
            \addlegendentry{$q_2$};
            % Curve and quiver+-
            \addplot[solid, thick, TolMutedBlue] table[col sep=comma, x=x, y=y] {data/ex2_rod_1_dense.csv};
            \addlegendentry{$\gamma_1$}
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{up}, v=\thisrow{vp}, scale arrows=\arrowscale}, -{Bar[width=4pt]}, TolMutedBlue, forget plot,
            ] table[col sep=comma] {data/ex2_rod_1_sparse.csv};
            \addplot[
                quiver={u=\thisrow{um}, v=\thisrow{vm}, scale arrows=\arrowscale}, -{Circle[length=2pt]}, TolMutedBlue, forget plot,
            ] table[col sep=comma] {data/ex2_rod_1_sparse.csv};
            % Plot the base points from CSV file
            \addplot[
                only marks, mark=*, mark size=.5pt, TolMutedBlue, forget plot,
            ] table[col sep=comma] {data/ex2_rod_1_sparse.csv};
            %
            %
            % Curve and quiver+-
            \addplot[solid, thick, TolMutedGreen] table[col sep=comma, x=x, y=y] {data/ex2_rod_2_dense.csv};
            \addlegendentry{$\gamma_2$}
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{up}, v=\thisrow{vp}, scale arrows=\arrowscale}, -{Bar[width=4pt]}, TolMutedGreen, forget plot,
            ] table[col sep=comma] {data/ex2_rod_2_sparse.csv};
            \addplot[
                quiver={u=\thisrow{um}, v=\thisrow{vm}, scale arrows=\arrowscale}, -{Circle[length=2pt]}, TolMutedGreen, forget plot,
            ] table[col sep=comma] {data/ex2_rod_2_sparse.csv};
            % Plot the base points from CSV file
            \addplot[
                only marks, mark=*, mark size=.5pt, TolMutedGreen, forget plot,
            ] table[col sep=comma] {data/ex2_rod_2_sparse.csv};
            %
            %
            % Curve and quiver+-
            \addplot[solid, thick, TolMutedPurple] table[col sep=comma, x=x, y=y] {data/ex2_rod_3_dense.csv};
            \addlegendentry{$\gamma_3$}
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{up}, v=\thisrow{vp}, scale arrows=\arrowscale}, -{Bar[width=4pt]}, TolMutedPurple, forget plot,
            ] table[col sep=comma] {data/ex2_rod_3_sparse.csv};
            \addplot[
                quiver={u=\thisrow{um}, v=\thisrow{vm}, scale arrows=\arrowscale}, -{Circle[length=2pt]}, TolMutedPurple, forget plot,
            ] table[col sep=comma] {data/ex2_rod_3_sparse.csv};
            % Plot the base points from CSV file
            \addplot[
                only marks, mark=*, mark size=.5pt, TolMutedPurple, forget plot,
            ] table[col sep=comma] {data/ex2_rod_3_sparse.csv};
        \end{axis}
    \end{tikzpicture}
    \caption{Three solution curves \(\gamma_1\) (blue), \(\gamma_2\) (green), and \(\gamma_3\) (purple) of a Lie group Heun method on the product of Lie groups \(\mathrm{SO}(2) \times \mathbb R^2\)
    modelling the movement within an electric field with two point charges located at
    $q_1$ (sand) and $q_2$ (olive). }
    \label{fig:Heun}
\end{figure}

>>>>

    \begin{tikzpicture}
        \begin{axis}[
            grid=major,
            width=.5\textwidth,
            legend style={at={(0.95,0.5)}, anchor=east},
            unit vector ratio=1 1,
            xmin = -1, xmax = 8,
            ymin = -4.25, ymax = 2.25,
            title style={yshift=-.5\baselineskip,},
            title={Trajectories of a charged rod between two point charges},
        ] %
            \addplot[only marks, mark=*, mark size=2pt, color=TolMutedSand] coordinates {(-0.5, 0.0)};
            \addlegendentry{$q_1$};
            \addplot[only marks, mark=*, mark size=2pt, color=TolMutedOlive] coordinates {(0.5, 0.0)};
            \addlegendentry{$q_2$};
            % Curve and quiver+-
            \addplot[solid, thick, TolMutedBlue] table[col sep=comma, x=x, y=y] {data/ex2_rod_1_dense.csv};
            \addlegendentry{$\gamma_1$}
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{up}, v=\thisrow{vp}, scale arrows=\arrowscale}, -{Bar[width=4pt]}, TolMutedBlue, forget plot,
            ] table[col sep=comma] {data/ex2_rod_1_sparse.csv};
            \addplot[
                quiver={u=\thisrow{um}, v=\thisrow{vm}, scale arrows=\arrowscale}, -{Circle[length=2pt]}, TolMutedBlue, forget plot,
            ] table[col sep=comma] {data/ex2_rod_1_sparse.csv};
            % Plot the base points from CSV file
            \addplot[
                only marks, mark=*, mark size=.5pt, TolMutedBlue, forget plot,
            ] table[col sep=comma] {data/ex2_rod_1_sparse.csv};
            %
            %
            % Curve and quiver+-
            \addplot[solid, thick, TolMutedGreen] table[col sep=comma, x=x, y=y] {data/ex2_rod_2_dense.csv};
            \addlegendentry{$\gamma_2$}
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{up}, v=\thisrow{vp}, scale arrows=\arrowscale}, -{Bar[width=4pt]}, TolMutedGreen, forget plot,
            ] table[col sep=comma] {data/ex2_rod_2_sparse.csv};
            \addplot[
                quiver={u=\thisrow{um}, v=\thisrow{vm}, scale arrows=\arrowscale}, -{Circle[length=2pt]}, TolMutedGreen, forget plot,
            ] table[col sep=comma] {data/ex2_rod_2_sparse.csv};
            % Plot the base points from CSV file
            \addplot[
                only marks, mark=*, mark size=.5pt, TolMutedGreen, forget plot,
            ] table[col sep=comma] {data/ex2_rod_2_sparse.csv};
            %
            %
            % Curve and quiver+-
            \addplot[solid, thick, TolMutedPurple] table[col sep=comma, x=x, y=y] {data/ex2_rod_3_dense.csv};
            \addlegendentry{$\gamma_3$}
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{up}, v=\thisrow{vp}, scale arrows=\arrowscale}, -{Bar[width=4pt]}, TolMutedPurple, forget plot,
            ] table[col sep=comma] {data/ex2_rod_3_sparse.csv};
            \addplot[
                quiver={u=\thisrow{um}, v=\thisrow{vm}, scale arrows=\arrowscale}, -{Circle[length=2pt]}, TolMutedPurple, forget plot,
            ] table[col sep=comma] {data/ex2_rod_3_sparse.csv};
            % Plot the base points from CSV file
            \addplot[
                only marks, mark=*, mark size=.5pt, TolMutedPurple, forget plot,
            ] table[col sep=comma] {data/ex2_rod_3_sparse.csv};
        \end{axis}
    \end{tikzpicture}
    \caption{Three solution curves \(\gamma_1\) (blue), \(\gamma_2\) (green), and \(\gamma_3\) (purple) of a Lie group Heun method on the product of Lie groups \(\mathrm{SO}(2) \times \mathbb R^2\)
    modelling the movement within an electric field with two point charges located at
    $q_1$ (sand) and $q_2$ (olive). }
    \label{fig:Heun}
\end{figure}
